A secondary screen architecture to accurately capture viewer interactions in interactive TV environments

### 2014-04-30 src/paper.tex
WIP: Added related work in introduction

The traditional remote control as a mechanism of interaction between viewer and TV can present notable problems.It is difficult to automatically identify the viewer in charge of the remote control. Thus, in practice the captured interactions are assigned to the whole group, rather than to individual viewers. As a result, in recommender systems applications for example, the tastes of the user in charge of the remote control can be imposed on the tastes of others.

@@

The proliferation of personal mobile devices has changed the people behaviors towards TV. Frequently people perform secondary tasks while watching TV such as use of email, use of social networks or surf the web. Many times these tasks are related to television watching where the viewer can evaluate, share or even recommend content to other people. Following this trend, more and more TV providers are enabling the audience to use personal devices as an extension of TV, i.e., as a secondary screen to enrich and immerse the user into the TV experience.

Identifying the viewers and capturing their interactions in TV environments are challenging activities~\cite{Hwang2007,Teixeira2010}.

to perform secondary tasks while watching TV

These tasks are frequently related to television watching e.g., evaluating content according to personal tastes, sharing, or even recommending content to other people. This paper presents an architecture that

TV family behaviors towards television.
potential use of mobile devices to capture individual user interactions.

>>>>

The traditional remote control as a mechanism of interaction between viewer and TV can present notable problems. It is difficult to automatically identify the viewer in charge of the remote control. Thus, in practice the captured interactions are assigned to the whole group, rather than to individual viewers. As a result, in recommender systems applications for example, the tastes of the user in charge of the remote control can be imposed on the tastes of others.

@@

The proliferation of personal mobile devices has changed the people behaviors towards TV. Frequently people perform secondary tasks while watching TV such as use of email and social networks or surf the web. Many times these tasks are related to television so that the viewer can evaluate, share or even recommend content to other people. Following this trend, TV providers are enabling the audience to use personal devices as an extension of TV, i.e., as a secondary screen to enrich and immerse the user into the TV experience.

In this scenario, secondary screen devices arise as a powerful mechanism to accurately capture viewer interactions. Other works addressed this separately: identifying viewers~\cite{Cabarcos2011,Hwang2007} and capturing interactions~\cite{Teixeira2010}. In this paper, we present a mechanism that uses

 without interfering in the viewing experience of other people in the TV environment

potential use of mobile devices to capture individual user interactions.
